%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%-----------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%-----------------------------------------------------------------------------

\documentclass[overlapped, 10pt]{res} % Section headers in flow (better for CV)
% \documentclass[marginmode, 10pt]{res} % Section headers in left margin (maybe preferred in compact resume)

\usepackage{hyperref} % Enable urls

\usepackage{hanging} % Provides the immensely useful ``hangparas'' hanging paragraph environment

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\usepackage[letterpaper, margin=0.5in]{geometry}   % Since we don't expect to publish a printed resume, we needn't such a large margin.

\renewcommand{\labelitemi}{\textendash}

% \setlength{\textwidth}{6.1in} % Text width of the document (tailored to marginmode)
\setlength{\textwidth}{7.0in} % Text width of the document (tailored to marginmode)
% \setlength{\textwidth}{7.5in} % Text width of the document (default)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|
% TAGGING
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|
\usepackage[dvipsnames]{xcolor}
\usepackage{amssymb}
\usepackage{pxfonts}
\usepackage{xstring}

% DEFINE TAG CHARACTERS
\newcommand{\physics}{$\blacktriangledown$}
\newcommand{\biochem}{$\varheartsuit$}
\newcommand{\shannon}{$\vardiamondsuit$}
\newcommand{\classic}{$\clubsuit$}
\newcommand{\quantum}{$\blacksquare$}
% DEFINE TAG COLORS
\newcommand{\physicscolor}{\color{YellowOrange}}
\newcommand{\biochemcolor}{\color{Emerald}}
\newcommand{\shannoncolor}{\color{Goldenrod}}
\newcommand{\classiccolor}{\color{Cyan}}
\newcommand{\quantumcolor}{\color{RedOrange}}

% TAG COMMANDS
\newcommand{\physicstag}{{\physicscolor\physics~}}
\newcommand{\biochemtag}{{\biochemcolor\biochem~}}
\newcommand{\shannontag}{{\shannoncolor\shannon~}}
\newcommand{\classictag}{{\classiccolor\classic~}}
\newcommand{\quantumtag}{{\quantumcolor\quantum~}}

% ALIGNED TAG COMMAND
\newcommand{\tag}[1]{
    {\IfSubStr{#1}{\physics}{\physicscolor}{\color{White}}\physics}
    {\IfSubStr{#1}{\biochem}{\biochemcolor}{\color{White}}\biochem}
    {\IfSubStr{#1}{\shannon}{\shannoncolor}{\color{White}}\shannon}
    {\IfSubStr{#1}{\classic}{\classiccolor}{\color{White}}\classic}
    {\IfSubStr{#1}{\quantum}{\quantumcolor}{\color{White}}\quantum}
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%-----------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%-----------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Kyle Sherbert} % Your name at the top

\moveleft.5\hoffset\vbox{\hrule width\textwidth height 1pt}%\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'

\moveleft.5\hoffset\centerline{ kmsherbert@yahoo.com \hfill (443) 975-3206 \hfill \href{kmsherbert.neocities.org}{kmsherbert.neocities.org} }


%-----------------------------------------------------------------------------

\begin{resume}

%-----------------------------------------------------------------------------
%	OBJECTIVE SECTION
%-----------------------------------------------------------------------------

\section{OBJECTIVE}

A theoretical position studying the fundamental role of information in physics.

%-----------------------------------------------------------------------------
%	PERSONAL STATEMENT SECTION
%-----------------------------------------------------------------------------

\section{STATEMENT}

Expert in multi-disciplinary sciences (\physicstag quantum physics, \biochemtag biochemistry, \shannontag information theory); algorithm development with \classictag classical and \quantumtag quantum computers; communicating arcane concepts through teaching and writing; and in walking to unwalkable places.


%-----------------------------------------------------------------------------
%	EDUCATION SECTION
%-----------------------------------------------------------------------------

\section{EDUCATION}

Ph.D - \textbf{Physics} \\
University of North Texas, Denton, TX \hfill exp. May 2022

MS - \textbf{Physics} \\
University of North Texas, Denton, TX \hfill  Dec 2020

MS - \textbf{Computer Science} \\
Towson University, Towson, MD \hfill May 2017

BS \textit{cum laude} - \textbf{Physics}; \textbf{Molecular Biology, Biochemistry and Bioinformatics} \\
Towson University, Towson, MD \hfill Aug 2015

%-----------------------------------------------------------------------------
%	PRESENTATIONS SECTION
%-----------------------------------------------------------------------------

\section{PRESENTATIONS}
\begin{itemize} \itemsep -2pt % Reduce space between items
\item[\tag{\shannon\quantum}-] Quantum compressive sensing.
    \hfill Talk, \textit{VTQ Internal Seminar}. 2022
    \\ \null \hfill Talk, \textit{SCaN Breakout Intern Seminar}. 2021
    \\ \null \hfill Talk, \textit{NASA/NRO Intern Symposium}. 2021
    \\ \null \hfill Talk, \textit{SCaN Intern Symposium}. 2021
\item[\tag{\physics\quantum}-] Band theory on a quantum computer.
    \hfill Invited Talk, \textit{ES22}. 2022
\item[\tag{\physics\biochem\shannon\quantum}-] Band theory and beyond.
    \hfill Poster, \textit{UNT MRS Poster Competition}. 2022
    \\ \null \hfill Talk, Sandia National Labs. 2022
    \\ \null \hfill Talk, Lawrence Berkeley National Labs. 2022
    \\ \null \hfill Talk, Dartmouth College. 2022
    \\ \null \hfill Talk, Virginia Tech. 2022
    \\ \null \hfill Dissertation defense. 2022
\item[\tag{\physics\quantum}-] Implementing Trans. Quantum Subspace Expansion with fewer qubits.
    \hfill Talk, \textit{APS March Meeting}. 2022
\item[\tag{\physics\biochem\quantum}-] Applying present-day quantum computers to materials science.
    \hfill Dissertation proposal. 2021
\item[\tag{\physics\quantum}-] Band structure in a quantum computer.
    \hfill Talk, \textit{APS March Meeting}. 2021
\item[\tag{\physics\quantum}-] A tutorial in variational quantum computing.
    \hfill End-of-term presentation. 2019
\item[\tag{\biochem}-] Seeking complexity in a nonlinear equilibrium chemical potential.
    \hfill Student lecture. 2019
\item[\tag{\physics}-] Predicting electron spin from scratch.
    \hfill End-of-term presentation. 2019
\item[\tag{\shannon\classic}-] Information reconciliation for erasure channels.
    \hfill Thesis defense. 2017
\item[\tag{\physics\shannon\classic}-] Information entropy of 1D quantum systems.
    \hfill Poster, \textit{TU Research Expo}. 2015
\item[\tag{}-] Surviving abroad without a smartphone.
    \hfill Poster, \textit{TU Honors College Expo}. 2015
\item[\tag{\biochem\classic}-] Exploring natural product formation with structural biology.
    \hfill Talk, \textit{MB3 Club Seminar}, 2015
    \\ \null \hfill Poster, \textit{CTRC Summer Research Colloquium}, 2014
    \\ \null \hfill Talk, \textit{HWI Weekly Seminar}, 2014
\item[\tag{\physics\classic}-] Computational simulation of electron diffraction.
    \hfill Poster, \textit{TU Research Expo}. 2014
    \\ \null \hfill Poster, \textit{APS March Meeting}. 2014
\end{itemize}

%-----------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%-----------------------------------------------------------------------------

\section{PUBLICATIONS}
\begin{itemize} \itemsep -2pt % Reduce space between items
\item[\tag{\shannon\quantum}-] Quantum compressive sensing: mathematical machinery...
    \hfill \href{https://arxiv.org/abs/2204.13035}{\textit{Appl. Sci.} (\textbf{12}: 15). 2022}
\item[\tag{\physics\biochem\shannon\quantum}-] Band theory and beyond: ... quantum algorithms for quantum chemistry.
    \hfill Poster and dissertation.* 2022
\item[\tag{\physics\quantum}-] Quantum algorithm for ... band structures with local tight-binding orbitals.
    \hfill \href{https://doi.org/10.21203/rs.3.rs-1318951/v1}{\textit{Scientific Reports (\textbf{12})}. 2022}
\item[\tag{\physics\quantum}-] A systematic ... band theory in a quantum computer.
    \hfill \href{https://arxiv.org/abs/2104.03409}{\textit{RSC Adv.} (\textbf{11}). 2021}
\item[\tag{\physics\quantum}-] Quantum computation of silicon ... band structure.
    \hfill \href{https://arxiv.org/abs/2006.03807}{\textit{Phys. Chem. Chem. Phys.} (\textbf{22}). 2020}
\item[\tag{\biochem}-] Seeking complexity in a nonlinear equilibrium chemical potential.
    \hfill Report.* 2019
\item[\tag{}-] Music theory: methods for mathematical music.
    \hfill Report.* 2018
\item[\tag{\classic}-] Hello, World!—Code Responsibly.
    \hfill \href{https://ieeexplore.ieee.org/document/8283486}{\textit{IEEE Security \& Privacy} (\textbf{16}: 1). 2018}
\item[\tag{\shannon\classic}-] Information reconciliation for erasure channels.
    \hfill Master's thesis.* 2017
\item[\tag{\physics\shannon\classic}-] Information entropy of 1D quantum systems.
    \hfill Poster and report.* 2015
\item[\tag{}-] Surviving abroad without a smartphone.
    \hfill Poster.* 2015
\item[\tag{\physics}-] An analysis of the PLAST model for quasars.
    \hfill Term paper.* 2014
\item[\tag{\shannon}-] The Circus Game.
    \hfill Pedagogical short story.* 2014
\item[\tag{\physics}-] Scarlet's Letters.
    \hfill Pedagogical short story.* 2014
\item[\tag{\biochem}-] Exploring natural product formation with structural biology.
    \hfill Poster and report.* 2014
\item[\tag{\physics\classic}-] Computational simulation of electron diffraction.
    \hfill Poster.* 2014
\end{itemize}

* Available on my personal website, \href{kmsherbert.neocities.org}{kmsherbert.neocities.org}

%-----------------------------------------------------------------------------
%	RESEARCH EXPERIENCE SECTION
%-----------------------------------------------------------------------------

\section{RESEARCH\\EXPERIENCE}

\textbf{Post-doctoral Researcher} \hfill Fall 2022-Present \\
\textit{Department of Physics, University of North Texas}, Denton, TX \\
Faculty Mentors: Nick Mayhall, Sophia Economou, Ed Barnes
\begin{itemize} \itemsep -2pt % Reduce space between items
\item[\tag{\physics\biochem\classic\quantum}-] Implemented optimized Julia code to simulate ctrl-VQE experiments.
\end{itemize}

\textbf{Doctoral Dissertation} \hfill Fall 2019-Spring 2022 \\
\textit{Department of Physics, University of North Texas}, Denton, TX \\
Faculty Mentor: Marco Buongiorno Nardelli
\begin{itemize} \itemsep -2pt % Reduce space between items
\item[\tag{\physics\biochem\shannon\quantum}-] Adapted quantum algorithms for quantum chemistry to solve problems in materials science (band structures) and information theory (compressive sensing).
\item[\tag{\physics\quantum}-] Developed novel strategy to locate excited states in variational quantum algorithms.
\item[\tag{\shannon\quantum}-] Developed quantum circuits and protocols for compressive sensing in a quantum computer.
\item[\tag{\physics\quantum}-] Developed three distinct quantum algorithms for band structure calculations using qiskit, cirq.
\item[\tag{\physics\quantum}-] Validated quantum algorithm using IBMQ Experience quantum computers.
\item[\tag{\physics\quantum}-] Derived statistical error for quantum variational excitation algorithm.
\item[\tag{}-] \textbf{Presented work} at \textit{UNT MRS Poster Competition} and numerous academic seminars.
\end{itemize}

\textbf{Virtual Intern} \hfill Summer 2021-Spring 2022 \\
\textit{NASA Goddard Space Flight Center}, Greenbelt, MD \\
Mentor: Harry Shaw
\begin{itemize} \itemsep -2pt % Reduce space between items
\item[\tag{\biochem\classic}-] Simulated molecular candidates for quantum oscillator in GAMESS.
\item[\tag{\shannon\quantum}-] Designed quantum compressive sensing protocol for LIDAR imaging with Born machines.
\item[\tag{\shannon\classic\quantum}-] Implemented classical approximation to quantum compressive sensing protocol using tensor networks in Python.
\item[\tag{\shannon\quantum}-] Developed quantum circuits and protocols for compressive sensing in a quantum computer.
\item[\tag{}-] \textbf{Presented work} in \textit{VTQ Internal Seminar} and multiple NASA seminars.
\item[\tag{}-] \textbf{Published article} in \textit{Appl. Sci.} (\textbf{12}).
\end{itemize}

\textbf{Research Assistant} \hfill Fall 2019-Spring 2022 \\
\textit{Department of Physics, University of North Texas}, Denton, TX \\
Faculty Mentor: Marco Buongiorno-Nardelli
\begin{itemize} \itemsep -2pt % Reduce space between items
\item[\tag{\physics\quantum}-] Developed novel strategy to locate excited states with variational quantum algorithms.
\item[\tag{\physics\quantum}-] Developed systematic quantum algorithm for band structure calculations using qiskit, cirq.
\item[\tag{\physics\quantum}-] Validated quantum algorithm using IBMQ Experience quantum computers.
\item[\tag{\physics\quantum}-] Calculated band structure of silicon with variational quantum eigensolver.
\item[\tag{\physics\quantum}-] Derived statistical error for quantum variational excitation algorithm.
\item[\tag{}-] \textbf{Presented work} at \textit{APS March Meeting 2021, 2022} and \textit{ES22} Invited Talk.
\item[\tag{}-] \textbf{Published articles} in \textit{Scientific Reports} (\textbf{12}), \textit{RSC Adv.} (\textbf{11}) and \textit{Phys. Chem. Chem. Phys.} (\textbf{22}).
\end{itemize}

\textbf{Research Assistant} \hfill Spring 2019 \\
\textit{Department of Physics, University of North Texas}, Denton, TX \\
Faculty Mentor: Paolo Grigolini
\begin{itemize} \itemsep -2pt % Reduce space between items
\item[\tag{\biochem\classic}-] Modeled and simulated non-linear Langevin dynamics of model enzyme reaction using Python.
\item[\tag{\biochem}-] Studied temporal complexity by approximating reaction wait-time distribution using stochastic calculus.
\item[\tag{}-] \textbf{Presented work} in student lecture for PHYS 6500.
\end{itemize}

\textbf{Research Assistant} \hfill Fall 2018 \\
\textit{Department of Physics, University of North Texas}, Denton, TX \\
Faculty Mentor: Marco Buongiorno-Nardelli
\begin{itemize} \itemsep -2pt % Reduce space between items
\item[\tag{\physics\classic}-] Investigated metamolecular dynamics of small Lennard-Jones clusters using Python.
\item[\tag{\quantum}-] Surveyed existing libraries for developing quantum algorithms.
\item[\tag{\physics\classic}-] Verified validity of Fourier differentiation in PAOFLOW electronic structure software.
\end{itemize}

\textbf{Master's Thesis} \hfill Fall 2016-Spring 2017 \\
\textit{Department of Computer and Information Sciences, Towson University}, Towson, MD \\
Faculty Mentor: Marius Zimand
\begin{itemize} \itemsep -2pt % Reduce space between items
\item[\tag{\shannon}-] Reviewed literature on Slepian-Wolf coding, information erasure reconciliation.
\item[\tag{\shannon\classic}-] Simulated information erasure reconciliation using various protocols using Python.
\item[\tag{\shannon\classic}-] Proposed novel probabilistic protocol for reconciling erasures.
\item[\tag{\shannon\classic}-] Measured protocol's empirical error-rate and optimal communication efficiency.
\item[\tag{\shannon}-] Approximated theoretical error-rate and optimal communication efficiency.
\end{itemize}

\textbf{Graduate Assistant} \hfill Fall 2015-Spring 2017 \\
\textit{Department of Computer and Information Sciences, Towson University}, Towson, MD \\
Faculty Mentors: Siddharth Kaza, Blair Taylor
\begin{itemize} \itemsep -2pt % Reduce space between items
\item[\tag{\classic}-] Created Data Hiding module for Security Injections repository.
\item[\tag{\classic}-] Designed and supervised development of Security Injections 3.0.
\item[\tag{\classic}-] Maintained web resources for Towson University's Cyber4All initiative.
\item[\tag{}-] Wrote NSF Grant Report assessing progress and project outlook.
\item[\tag{}-] \textbf{Published article} in \textit{IEEE Security and Privacy} article.
\end{itemize}

\textbf{Research Assistant} \hfill Spring 2015 \\
\textit{Dept. of Physics, Astronomy, and Geosciences, Towson University}, Towson, MD \\
Faculty Mentor: Jia-An Yan
\begin{itemize} \itemsep -2pt % Reduce space between items
\item[\tag{\physics\shannon\classic}-] Studied information entropy of scattering quantum systems using Matlab.
\item[\tag{\physics\shannon}-] Analytically solved information entropy of free particle as a function of time.
\item[\tag{\physics\shannon\classic}-] Replicated \textit{Phys. Rev. Lett.} work studying fractional revivals in bound quantum systems.
\item[\tag{}-] \textbf{Presented work} at 2015 Towson University Research Expo.
\end{itemize}

\textbf{Research Intern} \hfill Summer 2014 \\
\textit{Univeristy at Buffalo, Hauptman-Woodward Medical Research Institute}, Buffalo, NY \\
Principal Investigator: Andrew Gulick \\
Laboratory Mentor: Geoffrey Lippa
\begin{itemize} \itemsep -2pt % Reduce space between items
\item[\tag{\biochem}-] Performed site-directed mutagensis to introduce point mutations in \textit{E. coli} plasmid.
\item[\tag{\biochem}-] Mutated, expressed, and purified a bacterial enzyme for crystallization.
\item[\tag{\biochem}-] Conjectured reaction pathway based on product/byproduct elution patterns.
\item[\tag{\biochem\classic}-] Proposed deletion experiment based on predicted structure to test conjecture.
\item[\tag{}-] \textbf{Presented work} at \textit{HWI Weekly Seminar}, \textit{CTRC Summer Research Colloquium}, and \textit{MB3 Club Seminar}.
\end{itemize}

\textbf{Capstone Project} \hfill Winter 2014 \\
\textit{Dept. of Physics, Astronomy, and Geosciences, Towson University}, Towson, MD \\
Faculty Mentor: Jia-An Yan
\begin{itemize} \itemsep -2pt % Reduce space between items
\item[\tag{\physics\classic}-] Numerically solved Schr\"odinger's wave equation for a diffracting electron using Matlab.
\item[\tag{\physics\classic}-] Calculated reflection and transmission coefficients from energy transformation.
\item[\tag{\physics\classic}-] Compared optical Talbot effect with electron-beam analogue.
\item[\tag{}-] \textbf{Presented work} at \textit{APS March Meeting 2014} and \textit{TU Research Expo}.
\end{itemize}

%-----------------------------------------------------------------------------
%	TEACHING EXPERIENCE SECTION
%-----------------------------------------------------------------------------

\section{TEACHING\\EXPERIENCE}

\textbf{Instructor} \hfill Summers 2022-2023 \\
\textit{Center for Talented Youth, Johns Hopkins University}
\begin{itemize} \itemsep -2pt % Reduce space between items
\item[\tag{\classic}-] Developed curriculum for intensive summer course on \textit{Data Structures and Algorithms}.
\item[\tag{\classic}-] Delivered lectures, activities, and assignments for intensive and engaging three-week summer course.
\item[\tag{}-] Mentored a teaching assistant in developing communication and organization skills.
\item[\tag{}-] Tracked student progress in content, critical thinking, and engagement, for end-of-session evaluations.
\end{itemize}

\textbf{Online Instructor} \hfill Summer 2020-Spring 2022 \\
\textit{Center for Talented Youth, Johns Hopkins University}
\begin{itemize} \itemsep -2pt % Reduce space between items
\item[\tag{\classic}-] Guided students through asynchronous \textit{Programming in Python for Middle-school Students} online course.
\item[\tag{\classic}-] Tutored students all around the globe one-on-one in programming concepts and Python syntax.
\item[\tag{\classic}-] Executed, debugged, graded, and provided feedback on programming assignments.
\item[\tag{}-] Tracked student progress in content, critical thinking, and engagement, for end-of-course evaluations.
\end{itemize}

\textbf{Teaching Assistant} \hfill Fall 2018-Spring 2020 \\
\textit{Department of Physics, University of North Texas}, Denton, TX
\begin{itemize} \itemsep -2pt % Reduce space between items
\item[\tag{\physics}-] Assisted lecturer in \textit{Musical Acoustics} course with 100+ students.
\item[\tag{}-] Laboriously graded daily quizzes and quarterly exams.
\item[\tag{}-] Learned every student's name so they knew they were loved.
\item[\tag{}-] Adapted course format to online learning when global pandemic struck mid-semester.
\item[\tag{\physics}-] Facilitated labs for \textit{General Physics I}.
\item[\tag{\physics\classic}-] Supervised students in \textit{Computational Physics} and provided guidance as needed.
\end{itemize}

\textbf{Teaching Assistant} \hfill Summers 2015-2019 \\
\textit{Center for Talented Youth, Johns Hopkins University}
\begin{itemize} \itemsep -2pt % Reduce space between items
\item[\tag{\physics\biochem\shannon\classic}-] Assisted instructor in intensive summer courses for middle- and high-schoolers over many subjects: \textit{Astrophysics}, \textit{Fundamentals of Computer Science}, \textit{Cryptography}, \textit{Data Structures and Algorithms}, \textit{Genomics}, \textit{Investigations in Engineering}.
\item[\tag{\physics\biochem\shannon\classic\quantum}-] Organized ``lunchtime lessons'' for introducing students to non-curricular scientific topics of interest.
\item[\tag{}-] Tracked student progress in content, critical thinking, and engagement, for end-of-session evaluations.
\end{itemize}

\textbf{Substitute Teacher} \hfill Spring 2018 \\
\textit{Archdiocese of Washington} \\
\textit{Schools:} St. Mary of the Assumption Catholic School, Cardinal Hickey Academy
\begin{itemize} \itemsep -2pt % Reduce space between items
\item[\tag{\physics\biochem\classic}-] Taught Pre-K to 8th grade, all grades and all subjects, over four months.
\item[\tag{}-] Awakened Kindergarten students to world geography following the story of Jonah.
\item[\tag{\physics\biochem}-] Designed curriculum for three-day stint as SMA middle-school math and science teacher.
\item[\tag{}-] Substituted long-term for Spanish, all grades, at CHA.
\end{itemize}

\textbf{Graduate Assistant} \hfill Fall 2018-Spring 2020 \\
\textit{Department of Computer and Information Sciences, Towson University}, Towson, MD
\begin{itemize} \itemsep -2pt % Reduce space between items
\item[\tag{\classic}-] Assisted lecturer in \textit{General Computer Science} and \textit{Introduction to Computer Science I} courses.
\item[\tag{\classic}-] Supervised students in lab and provided guidance as needed.
\item[\tag{\classic}-] Executed, debugged, graded, and provided feedback on programming assignments.
\item[\tag{\classic}-] Tutored online high-school students enrolled in SPLASH program.
\end{itemize}

\textbf{Grader} \hfill Spring 2014 \\
\textit{Dept. of Physics, Astronomy, and Geosciences, Towson University}, Towson, MD
\begin{itemize} \itemsep -2pt % Reduce space between items
\item[\tag{\physics}-] Graded homeworks for \textit{Introductory Mathematical Physics}.
\item[\tag{\physics}-] Traced students' mistakes and provided consistent feedback.
\end{itemize}

%-----------------------------------------------------------------------------
%	ADDITIONAL EXPERIENCE SECTION
%-----------------------------------------------------------------------------

\section{ADDITIONAL\\EXPERIENCE}

\textbf{Church Choir} - Accompanist \hfill 2011-Present
\begin{itemize} \itemsep -2pt % Reduce space between items
\item[\tag{}-] Accompanied choir on clarinet, piano for weekly Catholic Mass.
\end{itemize}

\textbf{Denton Community Band, Blacksburg Community Band} - Clarinetist \hfill 2018-Present
\begin{itemize} \itemsep -2pt % Reduce space between items
\item[\tag{}-] Played clarinet in an ensemble for seasonal concerts and Santa Serenades.
\end{itemize}

\textbf{Christian Graduate Fellowship} - President \hfill 2018-2022 \\
\textit{University of North Texas}, Denton, TX
\begin{itemize} \itemsep -2pt % Reduce space between items
\item[\tag{}-] Organized weekly bible study and community night.
\end{itemize}

\textbf{Senior Software Developer} \hfill Fall 2017 \\
\textit{Department of Computer and Information Sciences, Towson University}, Towson, MD \\
Supervisor: Siddharth Kaza
\begin{itemize} \itemsep -2pt % Reduce space between items
\item[\tag{\classic}-] Designed database for CLARK cybersecurity curriculum management system using MongoDB, Angular.
\item[\tag{\classic}-] Developed CLARK microservice to suggest and search for learning outcomes.
\end{itemize}

\textbf{Society of Physics Students} \hfill 2012-2016 \\
\textit{Dept. of Physics, Astronomy, and Geosciences, Towson University}, Towson, MD
\begin{itemize} \itemsep -2pt % Reduce space between items
\item[\tag{\physics}-] Taught physics to young (age 6-10) students in Hampden Family Center.
\item[\tag{\physics}-] Demoed ``Shoot the Monkey'' station at 2016 \textit{Physics of Superheroes!} event.
\item[\tag{\physics}-] Magician's assistant in 2013 \textit{Physics is Magic!} Saturday Science show.
\end{itemize}

\textbf{College Scholarship Committee} - Student Representative \hfill 2015 \\
\textit{Jess and Mildred Fisher College of Science and Mathematics, Towson University}, Towson, MD
\begin{itemize} \itemsep -2pt % Reduce space between items
\item[\tag{}-] Selected 2015 recipients of Jess Fisher FCSM and Pre-Engineering Scholarships.
\end{itemize}

\textbf{Honors College Leadership Council} \hfill 2012-2014 \\
\textit{Honors College, Towson University}, Towson, MD
\begin{itemize} \itemsep -2pt % Reduce space between items
\item[\tag{}-] Organized college-prep event hosting AVID middle-schoolers at Honors College.
\item[\tag{}-] Organized ``Sweets, Stars, and Structure of the Universe'' planetarium event.
\item[\tag{}-] Redesigned Honors College Community page on Blackboard Learn.
\end{itemize}

%-----------------------------------------------------------------------------


%-----------------------------------------------------------------------------
%	AWARDS SECTION
%-----------------------------------------------------------------------------

\section{AWARDS}

U.S. Department of Energy Grant: DE-SC0019432 (Research Assistantship) \hfill 2019-2022 \\
UNT College of Science Travel Award \hfill 2020 \\
Maryland Space Grant Consortium Scholar \hfill 2014-2015 \\
Edward L. Rubendall Outstanding Physics Student \hfill 2012-2014 \\
Jess Fisher FCSM Scholar (Full Tuition) \hfill 2011-2015 \\
Maryland Distinguished Scholar \hfill 2011-2015 \\
Towson University Honors Scholar \hfill 2011-2015


%-----------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%-----------------------------------------------------------------------------

\section{COMPUTER\\SKILLS}

{\sl Languages:} Julia, Python (Anaconda), Java, JavaScript (Angular), Perl, Matlab, C/C++/C\# \\
{\sl Quantum:} Cirq (Google), Qiskit (IBMQ Experience), PyQuil (Rigetti Computing) \\
{\sl Chemistry:} GAMESS, MacMolPlt \\
{\sl Other:} Unix, LaTeX, Git, HTML5, CSS3


\end{resume}
\end{document}
